### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
failed attempt to include R results as numbers in text.

```{r Cleaning Replication Datasets Data}
##### Data already available, code does not need to be run!
### ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

@@

```{r Cleaning Coded Data}
##### Data already available, code does not need to be run!
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]

@@

```{r Check for Reliability and Validity Testability}
## Checking the measures to recalculate the reliability and factor analysis for.
## The question: "Are they psychometrics scales or not?", is key here.
View(coded_data_replications)

@@

```{r Final Preparation of Data}
### this code prepares the various pieces of data to be ready to use for the analyses.
## confirmatory analyses
# for hypothesis 4
data_H4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_H5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_H6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

# for hypothesis 1
data_H1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
# for hypothesis 2
data_H2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
# for hypothesis 3
data_H3_multiple <- Data_prep_H3_multiple(data_H5, data_H2)
data_H3_avg <- Data_prep_H3_avg(data_H5, data_H3_multiple)

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_H6)
# plot accompanying the results for Hypotheses 4, & 6
Plot_46_data <- data_prep_plot_46(data_H6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_H3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_H3_multiple)

### Exporting the final datasets for the analyses
# the open data
open_data(data = data_H4, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H4))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H4))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H4))), ".yml"))

open_data(data = data_H6, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H6))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H6))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H6))), ".yml"))

open_data(data = data_H5, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H5))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H5))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H5))), ".yml"))

open_data(data = data_H1, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H1))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H1))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H1))), ".yml"))

@@

open_data(data = data_H2, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H2))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H2))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H2))), ".yml"))

open_data(data = data_H3_multiple, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H3_multiple))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H3_multiple))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H3_multiple))), ".yml"))

open_data(data = data_H3_avg, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H3_avg))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H3_avg))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H3_avg))), ".yml"))

@@

# clearing up memory space by removing intermediate files from the environment
rm(coded_data_original, coded_data_original_shortened, coded_data_replications)

@@

```{r Hypothesis 1 Model}
# first some descriptives of reliability reporting
# Measurement type per original and replication:
H1_descriptive_table_1 <- table(data_H1$rep_org, data_H1$N_items)

# amount of reliability reported per original and replication 
# (given that measure is a multiple item measure):
H1_descriptive_table_2 <- table(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_type[data_H1$N_items == "multiple item measure"])

# New H1 test
# A chi square test for difference in N reliability reported for multiple 
# item measures.
H1_test_result <- chisq.test(data_H1$rep_org[data_H1$N_items == "multiple item measure"], data_H1$reliability_reported[data_H1$N_items == "multiple item measure"])

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```

```{r Hypothesis 2 Model}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H2))

# and same analyses for omega
# intercept only model to check the within and between group variance.
H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_H2[complete.cases(data_H2),]))

@@

```{r Hypothesis 3 Main Test}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
                                     family = binomial(), data = data_H3_avg))

# and for omega
H3_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
                                     omega.tot_avg, family = binomial(), 
                                     data = data_H3_avg))

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_H3_multiple))

# and for omega
H3_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1|g), family = 
                                                  binomial(), data = 
                                                  data_H3_multiple))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_H3_multiple))

# and for omega
H3_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1 + omega.tot|g), 
                                                family = binomial(), data =
                                                data_H3_multiple))

@@

$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$
```{r Hypothesis 6 Model}
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

  # adding the cfa results of one factor analysis to the results dataframe.
  cfa_results <- rbind(cfa_results, c(RMSEA_value, parallel_N_factors, 
                                      single_factor))
}
# removing the initial empty row
cfa_results <- cfa_results[-1,]

@@

## Descriptives

The mean sample size within the replications was 4844 participants (IQR = 3816). In the original articles the mean sample size was 244 (IQR = 140). In total, support was found for hypothesized effects of 34 of the 77 measures. Proportions of replication success per Many Labs project can be found in Table XXX.

@@

INSERT RELIABILITY REPORTING FLOW DIAGRAM FIGURE

@@

There are additional validity issues in measurement as the result of QMPs. While it is debatable whether or not $17.9\%$ average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications. This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity. In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure. The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessin]. Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.

>>>>

```{r Cleaning Replication Datasets Data, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

@@

```{r Cleaning Coded Data, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]

@@

```{r Check for Reliability and Validity Testability, include = FALSE}
## Checking the measures to recalculate the reliability and factor analysis for.
## The question: "Are they psychometrics scales or not?", is key here.
View(coded_data_replications)

@@

```{r Final Preparation of Data, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### this code prepares the various pieces of data to be ready to use for the 
### analyses.
## confirmatory analyses
# for hypothesis 4
data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_h5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

# for hypothesis 1
data_h1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
# for hypothesis 2
data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
# for hypothesis 3
data_h3_multiple <- Data_prep_H3_multiple(data_h5, data_h2)
data_h3_avg <- Data_prep_H3_avg(data_h5, data_h3_multiple)

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
Plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)

### Exporting the final datasets for the analyses
# the open data
open_data(data = data_h4, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h4))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h4))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h4))), ".yml"))

open_data(data = data_h6, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h6))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h6))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h6))), ".yml"))

open_data(data = data_h5, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h5))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h5))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h5))), ".yml"))

open_data(data = data_h1, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h1))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h1))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h1))), ".yml"))

@@

open_data(data = data_h2, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h2))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h2))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h2))), ".yml"))

open_data(data = data_h3_multiple, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h3_multiple))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h3_multiple))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h3_multiple))), ".yml"))

open_data(data = data_h3_avg, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h3_avg))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h3_avg))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h3_avg))), ".yml"))

@@

@@

```{r Hypothesis 1 Model}
# first some descriptives of reliability reporting
# Measurement type per original and replication:
H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)

# amount of reliability reported per original and replication 
# (given that measure is a multiple item measure):
H1_descriptive_table_2 <- table(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_type[data_h1$N_items == "multiple item measure"])

# New H1 test
# A chi square test for difference in N reliability reported for multiple 
# item measures.
H1_test_result <- chisq.test(data_h1$rep_org[data_h1$N_items == "multiple item measure"], data_h1$reliability_reported[data_h1$N_items == "multiple item measure"])

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
```{r Hypothesis 2 Model}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_h2))

# and same analyses for omega
# intercept only model to check the within and between group variance.
H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),]))

@@

```{r Hypothesis 3 Main Test}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
                                     family = binomial(), data = data_h3_avg))

# and for omega
H3_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
                                     omega.tot_avg, family = binomial(), 
                                     data = data_h3_avg))

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

# and for omega
H3_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1|g), family = 
                                                  binomial(), data = 
                                                  data_h3_multiple))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

# and for omega
H3_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1 + omega.tot|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

@@

$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$

```{r Hypothesis 6 Model}
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

  # adding the cfa results of one factor analysis to the results dataframe.
  cfa_results <- rbind(cfa_results, c(RMSEA_value, parallel_N_factors, 
                                      single_factor))
}

# removing the initial empty row
cfa_results <- cfa_results[-1,]

@@

## Descriptives
The mean sample size within the replications was `r printnum(round(mean(coded_data_replications$N, na.rm = TRUE)))` participants (IQR = `r printnum(round(IQR(coded_data_replications$N, na.rm = TRUE)))`). In the original articles the mean sample size was `r printnum(round(mean(coded_data_original_shortened$N, na.rm = TRUE)))` (IQR = `r printnum(round(IQR(coded_data_original_shortened$N, na.rm = TRUE)))`). In total, support was found for hypothesized effects of `r printnum(table(coded_data_replications$hypothesis_support)["Yes"])` of the `r printnum(nrow(coded_data_replications)` measures. Proportions of replication success per Many Labs project can be found in Table XXX.

@@

![Figure 1. Reliability reporting flow diagram](../../SupplementaryMaterials/reliability_reporting_flow_diagram.png)

@@

There are additional validity issues in measurement as the result of QMPs. While it is debatable whether or not $17.9\%$ average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications. This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity. In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure. The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessing]. Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.
